Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-09 snapshot_system/failover.tex

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south east
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{Global Dedup (VO), PDS FSB (VC)};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

@@

@@

\begin{table}
    \begin{tabular}{ll}
    Nodes Failed & Availability (\%) \\
    1           &  100\\
    2           & 100\\
    3          & 99.999\\
    5          & 99.993\\
    10          & 99.926\\
    20          & 99.295\\
    \end{tabular}
    \caption{Availability of a single block in the global data store}
    \label{tab:block-availability}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{Global Dedup (VO), PDS FSB (VC)};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=VMLinks] {figures/vo_vm_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=VMNonCDSLinks] {figures/vc_vm_links.txt};
		\addplot[color=red,densely dashed,mark=triangle*,mark size=3] table[x=VMs,y=VMCDSLinks] {figures/vc_vm_links.txt};
                \legend{VO FSB, Non-PDS FSB (VC), PDS FSB (VC)};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig-vm-links}
\end{figure}

@@

\begin{table}
    \begin{tabular}{|l|ll|}
    \hline
    \multirow{2}{*}{Nodes Failed}   & \multicolumn{2}{c|}{Availability(\%)}\\
                                    & $R=3$ & $R=4$\\
    \hline
    1           &  100      & 100\\
    2           & 100       & 100\\
    3          & 99.999     & 100\\
    5          & 99.993     & 99.9999\\
    10          & 99.926    & 99.995\\
    20          & 99.295    & 99.876\\
    \hline
    \end{tabular}
    \caption{Availability of a single FSB in the global data store with different relplication factors}
    \label{tab:fsb-availability}
\end{table}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \addplot[densely dashed, color=red,mark=none] table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \legend{$R=3$,$R=4$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig-fsb-availability}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
